Concrete compressive strength prediction with machine learning

### 2020-08-14 HarvardX_Data_Science_Capstone/capstone.Rmd
Save checkpoint xls file

>>>>

```{r dat-preparated-2, echo=F}
dat_preparated_2 <- dat
```

```{r dat-preparated-to-xls, echo=F}
dat_preparated_2 <- dat
names(dat_preparated_2) <-  gsub("day_", "", names(dat_preparated_2))
dat_preparated_2 <- dat_preparated_2 %>%
  gather("age", "Mpa", "3":"100", na.rm = TRUE, convert = TRUE)

write.xlsx(dat_preparated_2, "checkpoint.xls", sheetName = "Sheet1", 
  col.names = TRUE, row.names = TRUE, append = FALSE)
